### 2021-06-10 paper/report.tex
Add improved work scenario plot. Answer some comments.

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections are detected, which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms are turned on. Compared to the scenario with vaccinations only, this point is
reached around mid-May and it would be June for the comparison with the seasonality-only
scenario. The effect on total cases, however, is visible immediately. Despite the fact
that only a small fraction of the population performed weekly rapid tests in
March\footnote{8\% in the model; 27\% of respondents to the COSMO study reported in
    early March that they \textit{ever} did a rapid test)}, new
infections on April 1 would be reduced by 53\% relative to the scenario without
vaccinations, rapid tests, or seasonality.

@@

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.
\comment[id=HM]{Positive rates along the three channels might be nice here, if previous comment is not a quant story}
\comment[id=HM]{I think there is a story in here about risk conditional on past exposure vs. prospective risk in gatherings, but it is too late to work through it. We might just want to calculate the probabilities.}

>>>>

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections are detected, which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms are turned on. Compared to the scenario with vaccinations only, this point is
reached around mid-May and it would be June for the comparison with the seasonality-only
scenario. The effect on total cases, however, is visible immediately. Despite the fact
that only a small fraction of the population performed weekly rapid tests in
March\footnote{4\% to 6\% have done a rapid test within the last seven days in the first
week of March. 8\% in the model have ever done a rapid test at that point; 27\% of
respondents to the COSMO study reported in early March that they \textit{ever} did a
rapid test)}, new infections on April 1 would be reduced by 53\% relative to the scenario
without vaccinations, rapid tests, or seasonality.

@@

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.
\comment[id=HM]{Positive rates along the three channels might be nice here, if previous
comment is not a quant story}\comment[id=K]{Working on it}
\comment[id=HM]{I think there is a story in here about risk conditional on past exposure
vs. prospective risk in gatherings, but it is too late to work through it. We might just
want to calculate the probabilities.}\comment[id=K]{Yes, we have both in the private
reasons. Retrospective after a case in the household and prospective in anticipation of
participation in a weekly meeting with friends. However, we cannot easily turn these
separately on and off at the moment as they use the same multiplier. We could do,
however, do this in the future.}
